### 2016-07-05 abstract.tex

  Serializability is a well-understood correctness criterion that
  simplifies reasoning about the behavior of concurrent transactions
  by ensuring that transactions are \emph{isolated} from each other.
  However, enforcing serializable isolation comes at a steep cost in
  performance because it necessarily restricts opportunities to
  exploit concurrency even when such opportunities would not violate
  application-specific invariants. As a result, database systems in
  practice support, and often encourage, developers to use weaker
  alternatives. These alternatives break the strong isolation
  guarantees offered by serializable transactions to permit greater
  concurrency. Unfortunately, the semantics of weak isolation is
  poorly understood, and usually explained only informally in terms of
  low-level implementation artifacts. Consequently, verifying
  high-level correctness properties in such environments remains a
  challenging problem.

>>>>

  Serializability is a well-understood correctness criterion that
  simplifies reasoning about the behavior of concurrent transactions
  by ensuring that transactions are \emph{isolated} from each other
  while they execute.  However, enforcing serializable isolation comes
  at a steep cost in performance because it necessarily restricts
  opportunities to exploit concurrency even when such opportunities
  would not violate application-specific invariants. As a result,
  database systems in practice support, and often encourage,
  developers to use weaker alternatives. These alternatives break the
  strong isolation guarantees offered by serializable transactions to
  permit greater concurrency. Unfortunately, the semantics of weak
  isolation is poorly understood, and usually explained only
  informally in terms of low-level implementation
  artifacts. Consequently, verifying high-level correctness properties
  in such environments remains a challenging problem.

### 2016-07-05 introduction.tex

%%%SJ: tried to tighten this paragraph; the original now commented seemed overly
%%complicated
Recent results on reasoning about application invariants in the
presence of weak consistency~\cite{burckhardt14, redblueosdi,
redblueatc, ecinec, gotsmanpopl16} address broadly related concerns.
Weak consistency is a phenomenon that manifests on replicated data
stores, where atomic operations are concurrently executed against
different replicas, resulting in an execution order inconsistent with
%% We already say "inconsistent with.. ". 
any sequential order. In contrast, weak isolation is a property of
concurrent transactions interfering with one another resulting in an
execution order that is not serializable. Unlike weak consistency,
weak isolation can manifest even in an unreplicated setting, as
evident from the support for weakly-isolated transactions on
conventional (unreplicated) databases as mentioned above.  With the
added complexity of replication, richer mechanisms are needed to
reason about weak isolation in tandem with weak consistency. Thus,
frameworks for reasoning about weak isolation will necessarily have to
generalize the reasoning frameworks developed for weak consistency in
new and important ways.

>>>>

%%%SJ: tried to tighten this paragraph; the original now commented seemed overly
%%complicated
Recent results on reasoning about application invariants in the
presence of weak consistency~\cite{burckhardt14, redblueosdi,
redblueatc, ecinec, gotsmanpopl16} address broadly related concerns.
Weak consistency is a phenomenon that manifests on replicated data
stores, where atomic operations are concurrently executed against
different replicas, resulting in an execution order inconsistent with
%% We already say "inconsistent with.. ". 
any sequential order. In contrast, weak isolation is a property of
concurrent transactions interfering with one another resulting in an
execution order that is not serializable. Unlike weak consistency,
weak isolation can manifest even in an unreplicated setting, as
evident from the support for weakly-isolated transactions on
conventional (unreplicated) databases as mentioned above. In the
presence of replication, however, the interaction between weak
isolation and weak consistency can be subtle and non-trivial.
Understanding weak isolation in these varied contexts thus requires
new insights and substantial generalization of existing techniques.
